\section{Appendix}

\subsection{Join View TPCD Queries}
In our first experiment, we materialize the join of lineitem and orders.
We treat the TPCD queries as queries on the view, and we selected 12 out of the 22 to include in our experiments.
The other 10 queries did not make use of the join.

\subsection{Data Cube Specification}
We defined the base cube as a materialized view:
\begin{lstlisting}
select
  sum(l_extendedprice * (1 - l_discount)) as revenue,
  c_custkey, n_nationkey,
  r_regionkey, L_PARTKEY
from
  lineitem, orders,
  customer, nation,
  region
where
  l_orderkey = o_orderkey and
  O_CUSTKEY = c_custkey and
  c_nationkey = n_nationkey and
  N_REGIONKEY = r_regionkey

group by
  c_custkey, n_nationkey, 
  r_regionkey, L_PARTKEY
\end{lstlisting}

Each of queries was an aggregate over subsets of the dimensions of the cube, 
with a \sumfunc over the revenue column.
\begin{itemize}
\item Q1. all
\item Q2. c\_custkey
\item Q3. n\_nationkey
\item Q4. r\_regionkey
\item Q5. l\_partkey
\item Q6. c\_custkey,n\_nationkey
\item Q7. c\_custkey,r\_regionkey
\item Q8. c\_custkey,l\_partkey
\item Q9. n\_nationkey, r\_regionkey
\item Q10. n\_nationkey, l\_partkey
\item Q11. c\_custkey,n\_nationkey, r\_regionkey
\item Q12. c\_custkey,n\_nationkey,l\_partkey
\item Q13. n\_nationkey,r\_regionkey,l\_partkey
\end{itemize}

When we experimented with the median query, we changed the \sumfunc to a median of the revenues.

\subsection{Table Of TPCD Queries 2}
We denormalize the TPCD schema and treat each of the 22 queries as views on the denormalized schema.
In our experiments, we evaluate 10 of these with SVC. 
Here, we provide a table of the queries and reasons why a query was not suitable for our experiments.
The main reason a query was not used was because the cardinality of the result was small.
Since we sample from the view, if the result was small eg. < 10, it would not make sense to apply SVC.
Furthermore, in the TPCD specification the only tables that are affected by updates are lineitem and orders; and queries that
do not depend on these tables do not change; thus there is no need for maintenance.

Listed below are excluded queries and reasons for their exclusion.
\begin{itemize}
\item Query 1. Result cardinality too small
\item Query 2. The query was static
\item Query 6. Result cardinality too small
\item Query 7. Result cardinality too small
\item Query 8. Result cardinality too small
\item Query 11. The query was static 
\item Query 12. Result cardinality too small
\item Query 14. Result cardinality too small
\item Query 15. The query contains an inner query, which we treat as a view.
\item Query 16. The query was static 
\item Query 17. Result cardinality too small
\item Query 19. Result cardinality too small
\item Query 20. Result cardinality too small
\end{itemize}
