\documentclass{vldb}


\usepackage{enumitem}
\usepackage{framed}
\usepackage{cprotect}
\usepackage{enumitem}
\usepackage{listings}
\usepackage{amstext}
\usepackage{amstext}
\usepackage{pdfpages}
\usepackage{alltt}
\usepackage{epstopdf}
\usepackage{xspace,colortbl}
\usepackage[USenglish]{babel}
\usepackage{multirow}
\usepackage{url}
\usepackage{subfigure}
\usepackage{graphicx}%%
\usepackage{amssymb}
\usepackage{fmtcount}
\usepackage{amsfonts}
\usepackage{xspace}
\usepackage{amsmath}
\usepackage{multirow}
\usepackage[mathscr]{eucal}
%\usepackage{psfrag}
\usepackage{colortbl}
\usepackage{bm}
\usepackage{times}
\usepackage[nospace]{cite}
\usepackage{csquotes}

\lstset{basicstyle=\scriptsize,breaklines=true,language=SQL,belowcaptionskip=.1\baselineskip}

\linespread{0.945}

\makeatletter
\def\@copyrightspace{\relax}
\makeatother

\begin{document}

\setlength{\belowdisplayskip}{0.5pt} \setlength{\belowdisplayshortskip}{1pt}
\setlength{\abovedisplayskip}{0.5pt} \setlength{\abovedisplayshortskip}{1pt}
\setlength{\belowcaptionskip}{-10pt}
\selectfont

\newtheorem{theorem}{Theorem}
\newtheorem{example}{Example}
\newtheorem{definition}{Definition}
\newtheorem{problem}{Problem}
\newtheorem{property}{Property}
\newtheorem{proposition}{Proposition}
\newtheorem{lemma}{Lemma}
\newtheorem{corollary}{Corollary}

\newcommand{\cond}{\textrm{pred}\xspace}
\newcommand{\dataset}{data set\xspace}
\newcommand{\datasets}{data sets\xspace}
\newcommand{\spview}{\textsf{SPView}\xspace}
\newcommand{\fjview}{\textsf{FJView}\xspace}
\newcommand{\aggview}{\textsf{AggView}\xspace}
\newcommand{\hashfunc}[1]{\textsf{hash}(#1)\xspace}
\newcommand{\hashop}{\textsf{hash}\xspace}
\newcommand{\nsc}{\textsf{NormalizedSC}\xspace}
\newcommand{\rsc}{\textsf{RawSC}\xspace}

\newcommand{\avgfunc}{\ensuremath{\texttt{avg} }\xspace}
\newcommand{\maxfunc}{\ensuremath{\texttt{max} }\xspace}
\newcommand{\minfunc}{\ensuremath{\texttt{min} }\xspace}
\newcommand{\histfunc}{\ensuremath{\texttt{histogram\_numeric} }\xspace}
\newcommand{\countfunc}{\ensuremath{\texttt{count}}\xspace}
\newcommand{\sumfunc}{\ensuremath{\texttt{sum} }\xspace}
\newcommand{\varfunc}{\ensuremath{\texttt{var} }\xspace}
\newcommand{\stdfunc}{\ensuremath{\texttt{std} }\xspace}
\newcommand{\covfunc}{\ensuremath{\texttt{cov} }\xspace}
\newcommand{\corrfunc}{\ensuremath{\texttt{corr} }\xspace}
\newcommand{\medfunc}{\ensuremath{\texttt{median} }\xspace}
\newcommand{\percfunc}{\ensuremath{\texttt{percentile} }\xspace}
\newcommand{\havingfunc}{\ensuremath{\texttt{HAVING} }\xspace}
\newcommand{\selectfunc}{\ensuremath{\texttt{select} }\xspace}
\newcommand{\ratio}{\ensuremath{\rho }\xspace}


\newcommand{\insertion}{\ensuremath{\texttt{INSERT} }\xspace}
\newcommand{\update}{\ensuremath{\texttt{UPDATE} }\xspace}
\newcommand{\delete}{\ensuremath{\texttt{DELETE} }\xspace}

\newcommand{\svcfull}{Stale View Cleaning\xspace}
\newcommand{\svc}{SVC\xspace}
\newcommand{\svcnospace}{SVC}

\newcommand{\tbl}[1]{\textsf{#1}\xspace}
\newcommand{\field}[1]{\textsf{#1}\xspace}
\newcommand{\cost}{\textrm{cost}\xspace}
\newcommand{\ans}{\textsf{ans}\xspace}
\newcommand{\dans}{\Delta\textsf{ans}\xspace}
\newcommand{\cqp}{correction query processing\xspace}
\newcommand{\Cqp}{Correction query processing\xspace}

\newcommand{\reminder}[1]{{{\textcolor{magenta}{\{\{\bf #1\}\}}}\xspace}}
\newcommand{\specialcell}[2][c]{%
  \begin{tabular}[#1]{@{}c@{}}#2\end{tabular}}

\def\ojoin{\setbox0=\hbox{$\bowtie$}%
  \rule[-.02ex]{.25em}{.4pt}\llap{\rule[\ht0]{.25em}{.4pt}}}
\def\leftouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie}}
\def\rightouterjoin{\mathbin{\bowtie\mkern-5.8mu\ojoin}}
\def\fullouterjoin{\mathbin{\ojoin\mkern-5.8mu\bowtie\mkern-5.8mu\ojoin}}

%\setlength{\belowcaptionskip}{-10pt}

%\newcommand{\reminder}[1] {}
\pagestyle{plain}

\title{Stale View Cleaning: Getting Fresh Answers from Stale Materialized Views}

\numberofauthors{1}
\author{\large Sanjay Krishnan, Jiannan Wang, Michael J. Franklin, Ken Goldberg, Tim Kraska{$\,^\dag$} \\
\vspace{.2em}\affaddr{\large UC Berkeley, ~~ $^\dag$Brown University} \\
\vspace{.1em}\affaddr{\large \{sanjaykrishnan, jnwang, franklin, goldberg\}@berkeley.edu}\\
\affaddr{\large tim\_kraska@brown.edu}
}

%\fontsize{10pt}{12pt}
%\selectfont

\input{coverletter.tex}

\setcounter{page}{1}

\maketitle

\iffalse

\begin{abstract}
Materialized views, stored pre-computed query results, are used to facilitate queries on large datasets.
Materialized views can become out-date when base tables change and queries will give \emph{stale} results.
Maintaining materialized views has been well studied but is often very costly.
In this work, we model the view maintenance problem as a data cleaning problem and treat out-of-date rows materialized views as a type of data error.
In particular, we analyze the maintenance procedure for the views and infer how these updates affect a queries on a the stale view.
For common aggregate queries (\sumfunc, \countfunc, and \avgfunc), we can derive a correction factor from the sample to ``clean" the stale query result.
We bound our corrections in analytic confidence intervals, and in fact, we show that our technique is optimal with respect to estimate variance.
As sampling can be sensitive to long-tailed distributions, we further consider an outlier indexing technique to give increased accuracy when the data distributions are skewed.
We evaluate this approach on real and synthetic datasets and in both a single node (MySQL) and distributed environment (Apache Spark).
In one large scale experiment using 20-node Apache Spark cluster, we derived a 700,000,000 row view from a 1TB activity log base dataset.
We found that maintaining a 5\% sample was 16.3x faster than full maintenance yet only with mean query error of 1.2\%.
\end{abstract}
\fi

\vspace{-1em}

\begin{abstract}
Materialized views (MVs), stored pre-computed results, are widely used to facilitate fast queries on large datasets. When new records arrive at a high rate, it is infeasible to continuously update (maintain) MVs and a common solution is to defer maintenance by batching updates together. Between batches the MVs become increasingly stale with incorrect, missing, and superfluous rows leading to increasingly inaccurate query results.
We propose \svcfull (\svc) which addresses this problem from a data cleaning perspective. 
%We take inspiration from recent results in data cleaning which combine sampling and cleaning for accurate query processing. 
In \svc, we efficiently clean a sample of rows from a stale MV, and use the clean sample to estimate aggregate query results.
While approximate, the estimated query results reflect the most recent data.
As sampling can be sensitive to long-tailed distributions, we further explore an outlier indexing technique to give increased accuracy when the data distributions are skewed. \svc complements existing deferred maintenance approaches by giving accurate and bounded query answers between maintenance. We evaluate our method on a real dataset of workloads from the TPC-D benchmark and a real video distribution application.  Our experiments confirm our theoretical results: (1) cleaning an MV sample is more efficient than full view maintenance, (2) the estimated results are more accurate than using the stale MV, and (3) \svc is applicable for a wide variety of MVs.
\end{abstract}


\input{introduction.tex}
\input{problem_statement.tex}
\input{architecture.tex}
\input{correction.tex}
%\input{delta.tex}
\input{sampling.tex}
%\input{correction2.tex}
\input{outlier.tex}
%\input{analysis.tex}
\input{experiments.tex}
\input{conclusion.tex}\vspace{-1em}

\bibliographystyle{abbrv}
%\scriptsize
\fontsize{8.00pt}{8.5pt} \selectfont
\bibliographystyle{abbrv}
\bibliography{ref} 

%\input{appendix.tex}

\end{document}