% This is a simple LaTex sample document that gives a submission format
%   for IEEE PAMI-TC conference submissions.  Use at your own risk.

% Make two column format for LaTex 2e.\
\documentclass[12pt]{article} %,twocolumn

%\usepackage{times,amsmath,amsfonts}

% Use following instead for LaTex 2.09 (may need some other mods as well).
%\documentstyle[times,twocolumn]{article}
\usepackage[dvips]{graphicx,graphics}
% Set dimensions of columns, gap between columns, and paragraph indent
\setlength{\textheight}{10in} \setlength{\textwidth}{6in}
%\setlength{\columnsep}{0.3125in} \setlength{\topmargin}{0in}
\setlength{\headheight}{0in} \setlength{\headsep}{-1in}
\setlength{\parindent}{1pc}
\setlength{\oddsidemargin}{-.3in}  % Centers text.
\setlength{\evensidemargin}{-.3in}

% Add the period after section numbers.  Adjust spacing.
\newcommand{\Section}[1]{\vspace{-8pt}\section{\hskip -1em.~~#1}\vspace{-3pt}}
\newcommand{\SubSection}[1]{\vspace{-3pt}\subsection{\hskip -1em.~~#1}
        \vspace{-3pt}}
\newcommand{\bqn}{\begin{eqnarray}}
\newcommand{\eqn}{\end{eqnarray}}
\newcommand {\diff}[1] {\frac{\partial}{\partial #1}}
\newcommand{\jacob}[3]{\frac{\partial^2 #3}{\partial #1 \partial #2}}
\newcommand{\der}[2]{\frac{\partial #2}{\partial #1}}
\begin{document}

% Make title bold and 14 pt font (Latex default is non-bold, 16pt)
\title{Stat 471: Homework 03}
% For single author (just remove % characters)
\author{Moo K. Chung\\
mchung@stat.wisc.edu}
% For two authors (default example)
\maketitle \thispagestyle{empty}

{\bf Due Date:} October 27, 1:20pm. No late assignments will be
accepted or graded. There will be $10\%$ bonus points for
exceptional solutions.

\begin{enumerate}
\item  Estimate $p=P(X_1^2 + X_2^2 \geq 5)$ where $X_i$ are iid
$N(0,1)$ using simple Monte-Carlo integration technique.

\item Estimate the above probability using importance sampling
method. Show your importance sampling method gives a better
performance compared to the simple Monte-Carlo integration
technique.

\item Using $\tt{strength.data}$, test if the population variance
of arm strength is $\sigma^2=20^2$ at $\alpha = 0.1$ based on
Monte-Carlo simulation. Do not assume any parametric model.
Estimate the $90\%$ confidence interval for $\sigma^2$ based on
the simulation.

\item Based on the test used in Problem 3, estimate the type II
error and plot the statistical power based on Monte-Carlo
simulation. Comment on your plot.

\item Solve problem 3 using bootstrap. Use 200 bootstrap
replicates. Do not assume any parametric model. Compare your
result to that of problem 3.

\end{enumerate}

\end{document}
