\section{Streaming Progressive Correlation Clustering}
Given a graph $G = (V, E, W(e), M(v))$, we need to translate $G$ into actual changes to the tuples in the database.
In particular, we need to assign vertices to clusters -- each cluster represents an entity, and vertices in the cluster are duplicates of that entity.

We also want to provide low-latency intermediate results as the graph is updated in a streaming setting.

Currently, this is solved in SampleClean using connected components, which is prone to making significant errors in the presence of erroneous edges.

This problem has also been studied in the context of correlation clustering, a discrete optimization problem that attempts to find an assignment $\chi_{OPT}$ of vertices $v\in V$ to clusters satisfying
\[
\chi_{OPT} = \underset{\chi: V \rightarrow \mathbb{Z}}{\arg\min} \sum_{v \in V} \sum_{u \neq v} \mathbb{I}((u,v) \in E \oplus \chi(u) = \chi(v))
\]
where $\oplus$ is the exclusive-or operator.
That is, we wish to minimize the disagreements between the clustering $\chi$ and the graph $G$.

A simple randomized approximation algorithm is \emph{KwikCluster} [cite]. \reminder{Describe serial algorithm.}
\emph{KwikCluster} guarantees a 3 approximation, in expectation, to the correlation clustering problem for unweighted graphs.

However, this algorithm is serial and thus ill-suited for providing low-latency streaming results.
In this section, we explore parallel and streaming versions of KwikCluster.
Upon receiving a graph, the parallel KwikCluster implementation quickly returns a serializable clustering result;
as new vertices and edges are streamed in, the streaming algorithm updates the result in an eventually consistent fashion.

      \begin{algorithm}[h]
        \DontPrintSemicolon
        \caption{{\it KwikCluster}: serial peeling}
        \label{alg:seqgreedy}
        Init $\forall v\in V, \chi_{ser}(v) = \infty$\;
        Init $\forall v\in V, \gamma_{ser}(v) = $ UNASSIGNED\;
        \For {$i = 1$ to $n$}{
          Let $v$ be vertex such that $\pi(v) = i$.\;
          \If {$\gamma_{ser}(v) == $ UNASSIGNED}{
            $\gamma_{ser}(v) = $ CENTER\;
            $\chi_{ser}(v) = \pi(v)$\;
            \For {$u: (u,v) \in E^+$}{
              \If {$\gamma_{ser}(u) == $ UNASSIGNED}{
                $\gamma_{ser}(u) = $ SPOKE\;
                $\chi_{ser}(u) = \pi(v)$
              }
            }
          }
        }
      \end{algorithm}

\subsection{C4: Correlation Clustering using Concurrency Control}

We treat each set of KwikCluster operations on a vertex as an atomic transaction, and apply concurrency control mechanisms to ensure serializability.

C4 is guaranteed to be serializable.

      \begin{algorithm}[h]
        \DontPrintSemicolon
        \caption{{\it C4}: Parallel peeling}
        \label{alg:pargreedy}
        Init $\forall v\in V, \chi_{C4}(v) = \infty$\;
        Init $\forall v\in V, \gamma_{C4}(v) = $ UNASSIGNED\;
        \ParForAll{$p \in \{1, \ldots, P\}$}{
          \For {$i = p, p+P, \ldots, p + \lfloor n/P \rfloor P$}{
            \tcp{Transaction $T_v$}
            Let $v$ be vertex such that $\pi(v) = i$.\;
            \If {$\gamma_{C4}(v) == $ UNASSIGNED}{
              \tcp{Check concurrent neighbors}
              isCenter = {\scriptsize{\texttt{verifyIsCenter}}}($v$)\;
              \tcp{Create cluster}
              \lIf {isCenter}{
                {\scriptsize{\texttt{createCluster}}}($v$)
              }
            }
          }
        }
      \end{algorithm}

      \begin{algorithm}[h]
        \DontPrintSemicolon
        \caption{\texttt{verifyIsCenter($v$)}}
        \label{alg:verifyiscenter}
              \For {$u: (u,v) \in E^+$}{
                \If {$\pi(u) < \pi(v)$}{
                  \WaitUntil $\gamma_{C4}(u) \neq $ UNASSIGNED\;
                  \If {$\gamma_{C4}(u) == $ CENTER}{
                    return $false$
                  }
                }
              }
              return $true$
      \end{algorithm}
      \begin{algorithm}[h]
        \DontPrintSemicolon
        \caption{\texttt{createCluster($v$)}}
        \label{alg:createcluster}
        $\gamma_{C4}(v) = $ CENTER\;
        $\chi_{C4}(v) = \pi(v)$\;
        \For {$u: (u,v) \in E^+$}{
          \tcp{Atomic check \& set}
          \If {$\chi_{C4}(u) > \pi(v)$}{
            $\gamma_{C4}(u) = $ SPOKE;
            $\quad\chi_{C4}(u) = \pi(v)$
          }
        }
      \end{algorithm}


\subsection{EC3: Eventually Consistent Correlation Clustering}

